From textual to structured Web API Descriptions {\large Knowledge Discovery and Data Mining Seminar 2017}

### 2017-08-30 Paper/Paper_KDD.tex
small fixes

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}

@@

\title{From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017 }

\author{Selcuk~Aklanoglu,
        Han~Che,
        Caroline~Dieterich,
        Marcel~Ruoff,
        Jan-Peter~Schmidt  \\
Karlsruhe Institute of Technology \\
Sebastian~Bader \\
Department Applied Informatics and  Formal Description Methods (AIFB)  \\
Karlsruhe Institute of Technology

@@

$n$ is the total number of API descriptions and $df(d,t)$ the document frequency, the number of documents in which a term $t$ appears. 
With the TF-IDF Vectorizer, terms with a high term frequency but a low document frequency, have the highest tf-idf-value and can be considered more important than terms with a lower tf-idf-value. The result of the vectorization is a sparse matrix with \textcolor{red} {XXXXXXX} dimensions.

@@

This shows clearly, that our approach works and enables an useful new functionality. Nevertheless, there is a huge potential for improvements. First of all, more descriptions of an API needs to be collected. We think, that it will be very difficult, even impossible to automate this step. Our efforts to do so, were unfruitful. Another point, which can be optimized, is the manual clustering. It would be very interesting to see, which effect more manual clustered APIs as well more social-tagged APIs would have on the quality metrics. We assume that it will influence the Jaccard-Coefficient highly as stated in section \ref{sec:result}. And of course the search for the optimal parameter combination can be optimized. It is crucial, which interval is chosen for $k$. We chose a high interval and bigger steps between the $k$. Even running on a GPU, it took about an hour to run all the combinations in K-Means. To have better results, the steps need to be reduced, preferably to 1. But this would cause high computational costs. So, other approaches, for example like heuristic search could be evaluted.\\

>>>>

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}
\usepackage{setspace}

@@

\title{ From textual to structured Web API Descriptions {\large Knowledge Discovery and Data Mining Seminar 2017}}

\author{Selcuk~Aklanoglu,
        Han~Che,
        Caroline~Dieterich,
        Marcel~Ruoff,
        Jan-Peter~Schmidt,  \\
\textit{Karlsruhe Institute of Technology}  \\
Sebastian~Bader \\
\textit{Department Applied Informatics and  Formal Description Methods (AIFB),  \\
Karlsruhe Institute of Technology}

@@

$n$ is the total number of API descriptions and $df(d,t)$ the document frequency, the number of documents in which a term $t$ appears. 
With the TF-IDF Vectorizer, terms with a high term frequency but a low document frequency, have the highest tf-idf-value and can be considered more important than terms with a lower tf-idf-value. The result of the vectorization is a high dimensional sparse matrix.

@@

This shows clearly, that our approach works and enables an useful new functionality. Nevertheless, there is a huge potential for improvements. First of all, more descriptions of an API need to be collected. We think, that it will be very difficult, even impossible to automate this step. Our efforts to do so, were unfruitful. Another point, which can be optimized, is the manual clustering. It would be very interesting to see, which effect more manual clustered APIs as well more social-tagged APIs would have on the quality metrics. We assume that it will influence the Jaccard-Coefficient highly as stated in section \ref{sec:result}. And of course the search for the optimal parameter combination can be optimized. It is crucial, which interval is chosen for $k$. We chose a high interval and bigger steps between the $k$. Even running on a GPU, it took about an hour to run all the combinations in K-Means. To have better results, the steps need to be reduced, preferably to 1. But this would cause high computational costs. So, other approaches, for example like heuristic search could be evaluted.\\
